Measuring contrast processing in the visual system using SSVEP (and VEP?)

### 2024-04-02 review.qmd
More on fitting

@@

The sweep VEP (really, a sweep 'SSVEP') technique is now commonly-used to obtain a rapid and objective measurement of visual acuity. In particular, because of its relative speed and simplicity, this technique has now become a standard for conducting tests of visual acuity in very young subjects or where behavioural tests are not appropriate [@Ridder2004 Diva vs Enfant, @Hoffman, @Bach and @Farmer].
The sweep VEP (really, a sweep 'SSVEP') technique is now commonly-used to obtain a rapid and objective measurement of visual acuity. In particular, because of its relative speed and simplicity, this technique has now become a standard for conducting tests of visual acuity in very young subjects or where behavioural tests are not appropriate [@Ridder2004; @Hoffman; @Bach; @Farmer].

>>>>

The complexity of even a simple simulation of the frequency-domain signal arising from non-linear interactions is intriguing. Presumably, the signal measured from early visual cortex contains is the result of a cascade of nonlinear retinal and cortical operations up to that point and therefore contains a 'signature' of the computational nature, order and parameters of those operations - including the shape of the transducer functions and the computations involved in signal combination. In principle, that information could be recovered from the SSVEP signal.

This possibility was recognised in the early days of the technique [@reganandRegan1988]. Although characterising the complete set of computations along entire processing pathway is problematic, careful parametric variation of the input stimuli does allow us to fit models of early visual gain control using SSVEP data. ... MORE HERE - Although this idea was suggested as early as 1988 (probably earlier) not many people seem to have done it much. Candy and Norcia (in infants) 2001, Busse et al2008, Tsai/Norcia/Wade 2010s, Then lots of Baker stuff including the CerebCort paper. : Focusing only on SSVEP: [@NorciaCandy2001, @Regan1990?  ]

@@

The sweep VEP (technically, the sweep 'SSVEP') technique is now commonly-used to obtain a rapid and objective measurement of visual acuity. Because of its relative speed and simplicity, this technique has now become a standard for conducting tests of visual acuity in very young subjects or where behavioural tests are not appropriate [@Ridder2004 Diva vs Enfant, @Hoffman, @Bach and @Farmer].
The sweep VEP (really, a sweep 'SSVEP') technique is now commonly-used to obtain a rapid and objective measurement of visual acuity. In particular, because of its relative speed and simplicity, this technique has now become a standard for conducting tests of visual acuity in very young subjects or where behavioural tests are not appropriate [@Ridder2004; @Hoffman; @Bach; @Farmer].

##
